THESIS TITLE

### 2023-07-16 msthesis.tex
simulation draft complete

\subsection{$L_{out}$ Optimization For Single \e}
Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$. Then sweep the $t_{out}$ parameter to find the optimal value.
This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.

@@

\subsection{$\phi_{lag}$ Optimization For Bunches}
After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
They were modeled as $N$ electrons fired from an \e gun at even time intervals. This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \caption{An Illustration of first GUI design.}
    \label{fig:gui_illustration}
\end{figure}

@@

>>>>

\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$. Then sweep the $t_{out}$ parameter to find the optimal value.
This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.

@@

\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
They were modeled as $N$ electrons fired from an \e gun at even time intervals. This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \caption{An Illustration of the first GUI design.}
    \label{fig:gui_illustration}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
    \caption{The configuration frame of implementated first GUI design.}
    \label{fig:gui_config}
\end{figure}

@@

In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;

\subsubsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.

\subsubsection{Simulation Frame}
This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
    \caption{Simulate frame of \textit{GUI}.}
    \label{fig:gui_simulate_1}
\end{figure}

\subsubsection{Render Frame}
Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.

\begin{figure}
    \centering
    \captionsetup{justification=centering}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
    \end{subfigure} 
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
    \end{subfigure} 
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

\subsubsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
    \caption{Analyze frame of \textit{GUI} E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

\begin{figure}
    \centering
    \captionsetup{justification=centering}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
    \end{subfigure} 
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
    \end{subfigure} 
    \caption{Analyze frame of \textit{GUI} E(t).}
    \label{fig:gui_analyze_Et}
\end{figure}

\subsubsection{Sweep Frame}
Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
$\phi_{lag}$ sweep was the first parameter to be implemented. 
It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
    \label{fig:gui_sweep_running}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
    \label{fig:gui_sweep_sR}
\end{figure}

As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
New analysis and sweep features will be implemented and current capabilities will be improved in the near future.

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
simulation draft complete

In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} 
\begin{itemize}
    \item[Configuration Frame] provides an interface for specifying, saving or loading a configuration.
    \item[Simulation Frame] provides an interface for starting and managing the \textit{simulation engine}, displaying the progress of the simulation.
    \item[Render Frame] provides an interface for rendering the results of a simulation.
    \item[Analyze Frame] provides an interface for analyzing the results of a simulation.  
    \item[Sweep Frame] provides an interface for parameter sweep functionality. 
\end{itemize}

\subsubsection{Configuration Frame}
This frame consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.

\subsubsection{Simulation Frame}
This frame spawns the \textit{simulation engine}, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
    \caption{Simulate frame of \textit{GUI}.}
    \label{fig:gui_simulate_1}
\end{figure}

@@

\begin{figure}
    \centering
    \captionsetup{justification=centering}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
    \end{subfigure} 
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
    \end{subfigure} 
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

\subsubsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.

\subsubsection{Sweep Frame}

>>>>

In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;

\subsubsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.

\subsubsection{Simulation Frame}
This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
    \caption{Simulate frame of \textit{GUI}.}
    \label{fig:gui_simulate_1}
\end{figure}

@@

\begin{figure}
    \centering
    \captionsetup{justification=centering}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
    \end{subfigure} 
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
    \end{subfigure} 
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

\subsubsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
    \caption{Analyze frame of \textit{GUI} E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

\begin{figure}
    \centering
    \captionsetup{justification=centering}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_1.png}
    \end{subfigure} 
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_2.png}
    \end{subfigure} 
    \caption{Analyze frame of \textit{GUI} E(t).}
    \label{fig:gui_analyze_Et}
\end{figure}

\subsubsection{Sweep Frame}
Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
$\phi_{lag}$ sweep was the first parameter to be implemented. 
It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_running.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
    \label{fig:gui_sweep_running}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sR.png}
    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
    \label{fig:gui_sweep_sR}
\end{figure}

As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
